---
title: "Grads On The Go Report for <br /> `r params$NE_institutions`"
params: 
  NE_institutions: "University of Nebraska at Kearney"
output: 
  html_document:
    theme: cerulean
---

<style type="text/css">
h1.title {
  font-size: 38px;
  text-align: center;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# ---------------------------------------------------#
# Package loading and data import
# ---------------------------------------------------#

library(pacman)
p_load("dplyr", "haven", "stats", "kableExtra", install = T)

GOTG_Data <- read_dta('/Users/jayjeffries/Desktop/R Resources/Parameterized Reporting/InstitutionFile.dta')

# ---------------------------------------------------#
# Filtering data by parameters
# ---------------------------------------------------#

GOTG_report_data <- GOTG_Data %>%
  filter(instnm == params$NE_institutions)

GOTG_report_data <- as.data.frame(GOTG_report_data)
GOTG_report_data$npt4_avg <- format(GOTG_report_data$npt4_avg, scientific=F)
```

|           This report is made up of data from *Grads on the Go* (2011-2018) which measures college-specific labor markets for graduates through use of *LinkedIn* account information along with *Integrated Postsecondary Education Data System* (IPEDS) and the *College Scorecard* data from the U.S. Department of Education. This summary report is for the `r params$NE_institutions`. 

```{r, echo = F}
# ---------------------------------------------------#
# Defining the contents of the three summary tables
# ---------------------------------------------------#

SummaryTable1 = GOTG_report_data %>%
  summarise( 
    "% Alums in State" = round(GOTG_report_data[, 6], 2),
    "Alums Avg Miles from Institution" = round(GOTG_report_data[, 9], 2),
    "Avg Hourly Wage of BA Grad" = round(GOTG_report_data[, 10], 2),
    "Associates Degrees Completed" = round(GOTG_report_data[, 22], 2),
    "Bachelor's Degrees Completed" = round(GOTG_report_data[, 23], 2),
    "Master's Degrees Completed" = round(GOTG_report_data[, 24], 2),
    "Doctorate Degrees Completed" = round(GOTG_report_data[, 26], 2),
  )

SummaryTable2 = GOTG_report_data %>%
  summarise( 
    "Avg Full-Time Enrollment (FTE)" = round(GOTG_report_data[19], 0),
    "Black Undergrads" = paste("%", round(GOTG_report_data[, 33], 2)*100),
    "Hispanic Undergrads" = paste("%", round(GOTG_report_data[, 34], 2)*100),
    "Asian Undergrads" = paste("%", round(GOTG_report_data[, 35], 2)*100),
    "Women Undergrads" = paste("%", round(GOTG_report_data[, 36], 2)*100)
  )

SummaryTable3 = GOTG_report_data %>%
  summarise( 
    "Avg Net Cost of Attendance" = paste("$", GOTG_report_data$npt4_avg),
    "Undergrads with Federal Loans" = paste("%", round(GOTG_report_data$pctfloan_avg, 2)*100),
    "Undergrads with Pell Grants" = paste("%", round(GOTG_report_data$pctpell_avg, 2)*100),
    "Avg Instructional Expenditure per FTE" = paste("$", round(GOTG_report_data$inexpfte_avg, 2)),
  )

# ---------------------------------------------------#
# Designing and organizing tables for each summary table
# ---------------------------------------------------#

Summary1 <- kbl(SummaryTable1, caption = "Table 1. Alumni Summary Statistics", align = 'c') %>%
  add_header_above(c("Alum Statistics" = 3, 
                     "Degree Statistics" = 4)) %>%
  row_spec(0, bold = TRUE, hline_after = T) %>% 
  kable_paper("hover", font_size = 13, full_width = TRUE) %>%
  kable_styling(html_font = "serif", row_label_position = "c")

Summary2 <- kbl(SummaryTable2, caption = "Table 2. Institution Demographics", align = 'c') %>%
  add_header_above(c("Student Demographics" = 5)) %>%
  row_spec(0, bold = TRUE, hline_after = T) %>% 
  kable_paper("hover", font_size = 13, full_width = TRUE) %>%
  kable_styling(html_font = "serif", row_label_position = "c")

Summary3 <- kbl(SummaryTable3, caption = "Table 3. Financial Demographics", align = 'c') %>%
  add_header_above(c("Price" = 1, "Student Funding" = 2, "Expenditures" = 1)) %>%
  row_spec(0, bold = TRUE, hline_after = T) %>% 
  kable_paper("hover", font_size = 13, full_width = TRUE) %>%
  kable_styling(html_font = "serif", row_label_position = "c")

# ---------------------------------------------------#
# Printing all 3 summary tables
# ---------------------------------------------------#

Summary1
Summary2
Summary3
```
