---
title: "Social Capital Atlas Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params: 
  NE_highschools: "68504"
output:
  prettydoc::html_pretty:
    theme: architect
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load("ggplot2", "geomtextpath", "dplyr", "readr", "stats", "prettydoc", "patchwork", install = T)

SC_Data <- read_csv('/Users/jayjeffries/Desktop/R Resources/Parameterized Reporting/SC Example/social_capital_high_school.csv')

# ---------------------------------------------------#
# Filtering data by parameters
# ---------------------------------------------------#

SC_report_data <- SC_Data %>%
  filter(zip == params$NE_highschools)

# ---------------------------------------------------#
# Labeling `r` objects for in-text use
# ---------------------------------------------------#

highschool_zip <- format(SC_report_data$zip, scientific = F, digits = 5)
highschool_size <- SC_report_data$students_9_to_12
highschool_name <- SC_report_data$high_school_name

xavg <- mean(SC_Data$ec_high_parent_ses_hs, na.rm = T)
yavg <- mean(SC_Data$volunteering_rate_hs, na.rm = T)
volunteer <- round(SC_report_data$volunteering_rate_hs, 3) * 100

# ---------------------------------------------------#
# Creating column to indicate NE schools (1) and non-NE schools (0)
# ---------------------------------------------------#

SC_Data$color <- ifelse(SC_Data$zip >= 68001 & SC_Data$zip <= 69376, 1, 0)
SC_Data$color <- factor(SC_Data$color, labels = c("Non-Nebraska School", "Nebraska School"))
```
# Summary

|          This report derives from the Social Capital Atlas project developed in collaboration with *Meta*, *Opportunity Insights*, and researchers from Harvard, New York University, and Stanford ^[Chetty, R., Jackson, M. O., Kuchler, T., Stroebel, J., Hendren, N., Fluegge, R. B., Gong, S., Gonzalez, F., Grondin, A., Jacob, M., Johnston, D., Koenen, M., Laguna-Muggenburg, E., Mudekereza, F., Rutter, T., Thor, N., Townsend, W., Zhang, R., Bailey, M., … Wernerfelt, N. (2022). Social capital I: Measurement and associations with economic mobility. Nature, 608(7921), 108–121. https://doi.org/10.1038/s41586-022-04996-4]. These data are nested at the highschool level. Using 21 billion riendships found from publicly available *Facebook* account information and the National Center for Education Statistics (NCES) data, SES and identify social capital constructs in students were analyzed^[[Dataset](https://data.humdata.org/dataset/social-capital-atlas)]. Measured variables include:

* Baseline measures of SES found by combining proxies for SES (e.g., median incomes in one’s residential ZIP code, cell phone model, college attended, etc.) observed on Facebook.
* The constructs of connectedness, cohesiveness, and civic engagemennt^[[Social Capital Website](https://www.socialcapital.org/?dimension=EconomicConnectednessIndividual&dim1=EconomicConnectednessIndividual&dim2=CohesivenessClustering&dim3=CivicEngagementVolunteeringRates&geoLevel=hs&selectedId=317284001032)]. 

> This document is in reference to _**`r highschool_name`**_ in the zip code `r highschool_zip`. 
There are currently `r highschool_size` students enrolled at `r highschool_name`. 
Of these students, `r volunteer`% of students volunteer. 

```{r scatterplots, echo=FALSE, message = F, warning = F, fig.align = 'c', out.width= "90%"}
# ---------------------------------------------------#
# National data scatterplot of high parental SES & student volunteering rate
# ---------------------------------------------------#

ggplot(SC_Data |> arrange(color), 
       aes(x = ec_high_parent_ses_hs, y = volunteering_rate_hs)) + 
  geom_point(aes(color = factor(color), position = "jitter")) + 
  scale_colour_manual(values = c("#02075d", "#2E5A88")) +
  # scale_fill_manual(values = c("#000080", "lightblue")) +
  labs(x = "Share of High Parental SES (%)", y = "Volunteering Rate of Students (%)") + 
  geom_textvline(label = "National Average", xintercept = xavg, 
                 linetype = "dotted", color = "darkgray", fontface = "bold", size = 5.5) +
  geom_texthline(label = "National Average", yintercept = yavg, 
                 linetype = "dotted", color = "darkgray", fontface = "bold", size = 5.5) +
  ggtitle("Figure 1. Scatterplot of High Parental SES and Volunteering, National Data") +
  guides(color = guide_legend(override.aes = list(size = 8))) +
  theme_light() +
  theme(plot.title = element_text(face = "bold", hjust = .1), panel.background = element_blank(), 
        legend.title=element_blank())

# ---------------------------------------------------#
# Specifying Lincoln data via zipcodes
# ---------------------------------------------------#

SC_Lincoln_data <- SC_Data[(SC_Data$zip == "68504" | 
                            SC_Data$zip ==  "68512" |
                            SC_Data$zip == "68510.1" | 
                            SC_Data$zip == "68510.2" |
                            SC_Data$zip == "68510" |
                            SC_Data$zip == "68507" | 
                            SC_Data$zip == "68506" |
                            SC_Data$zip == "68803"),]

# ---------------------------------------------------#
# Lincoln data scatterplot of high parental SES & student volunteering rate
# ---------------------------------------------------#

ggplot(SC_Lincoln_data, aes(x = ec_high_parent_ses_hs, y = volunteering_rate_hs)) + 
  geom_point(position = "jitter") +
  labs(x = "Share of High Parental SES (%)", y = "Volunteering Rate of Students (%)") + 
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "#2E5A88") +
  geom_text(aes(label = as.character(high_school_name)), hjust = 0, vjust = 1.35) +
  expand_limits(x = c(1, 1.6)) +
  geom_textvline(label = "National Average", xintercept = xavg, linetype = "dotted", alpha = .55, size = 5.5) +
  geom_texthline(label = "National Average", yintercept = yavg, linetype = "dotted", alpha = .55, size = 5.5) +
  ggtitle("Figure 2. Scatterplot of High Parental SES and Volunteering, Local Data") +
  theme_light() +
  theme(plot.title = element_text(face = "bold", hjust = 0.5), panel.background = element_blank())
```

|          Share of high parental SES is defined as: two times the share of high-parental-SES friends (who attended the same school within three birth cohorts of the individual) among high-parental-SES individuals, averaged over all high parental-SES individuals in the school. "High SES" is quantified as being above median income.

```{r, eval = T}
# ---------------------------------------------------#
# Sandbox - doing some "extras" with data out of personal interests
# ---------------------------------------------------#

filter(SC_Data, ec_high_parent_ses_hs == max(ec_high_parent_ses_hs, na.rm = T))
filter(SC_Data, ec_high_parent_ses_hs == min(ec_high_parent_ses_hs, na.rm = T))

filter(SC_Data, volunteering_rate_hs == max(volunteering_rate_hs, na.rm = T))
filter(SC_Data, volunteering_rate_hs == min(volunteering_rate_hs, na.rm = T))

NE_Data <- filter(SC_Data, color == 1)
filter(NE_Data, ec_high_parent_ses_hs == max(ec_high_parent_ses_hs, na.rm = T))
filter(NE_Data, volunteering_rate_hs == max(volunteering_rate_hs, na.rm = T))
```
