---
title: "State Education Summary Report for `r params$State`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: tactile
params: 
  State: "AK"
---
```{r, include = F}
knitr::opts_chunk$set(echo = TRUE)

# ---------------------------------------------------#
# Package loading and data import
# ---------------------------------------------------#

library(pacman)
p_load("ggplot2", "kableExtra", "dplyr", "readr", "stats", "readxl", "geomtextpath", "labelled", "patchwork", install = T)

StateEd_Data <- read_excel("/Users/jayjeffries/Desktop/R Resources/Parameterized Reporting/State Ed Example/HSDistrict_Data.xlsx")

State_ACT_Data <- read_excel("/Users/jayjeffries/Desktop/R Resources/Parameterized Reporting/State Ed Example/State_ACT.xls")

# ---------------------------------------------------#
# Filtering data by parameters
# ---------------------------------------------------#

HS_State <- params$State

StateHS_Data <- StateEd_Data |>
  select("SCH_NAME", "CITY", "STATE", "CHARTER", "MAGNET", "TITLE_1_WIDE", "STUDENTS", "TEACHERS", "RATIO") |>
  filter(STATE == HS_State)

# bar chart data (for later)
barch_data <- State_ACT_Data |>
  filter(State == params$State | State_Full == "United States")

# ---------------------------------------------------#
# Re-labeling variables to proper names
# ---------------------------------------------------#

var_label(StateHS_Data$SCH_NAME) <- "School Name"
var_label(StateHS_Data$CITY) <- "City"
var_label(StateHS_Data$CHARTER) <- "Charter"
var_label(StateHS_Data$MAGNET) <- "Magnet"
var_label(StateHS_Data$TITLE_1_WIDE) <- "Title 1 School"
var_label(StateHS_Data$STUDENTS) <- "Number of Students"
var_label(StateHS_Data$TEACHERS) <- "Number of Teachers"
var_label(StateHS_Data$RATIO) <- "Student-Teacher Ratio"

# ---------------------------------------------------#
# Labeling `r` objects for in-text use
# ---------------------------------------------------#

state_name <- barch_data$State_Full[2]
teachers <- round(mean(StateEd_Data$TEACHERS, na.rm = T),0)
students <- round(mean(StateEd_Data$STUDENTS, na.rm = T),0)
ratio <- round(mean(StateEd_Data$RATIO, na.rm = T),0)
```

## Overview

Using high school and ACT data from the [National Center for Educational Statistics](https://nces.ed.gov/ccd/schoolsearch/) (*NCES*), a report was created to describe the state of `r state_name`'s education systems. 

* A table (Table 1) of descriptive high-school statistics for `r state_name`. These can be compared with the following national averages:
  * The average number of teachers reported in U.S. high schools is **`r teachers` teachers**.
  * The average number of students reported in U.S. high schools is **`r students` students**.
  * The average student:teacher ratio reported in U.S. high schools is **`r ratio` students to teachers**.
* Charts (Figures 1-5) of `r state_name`'s ACT scores.

## State Education Descriptives

```{r, echo = F, fig.align = 'c'}
# ---------------------------------------------------#
# Defining the contents of the summary table
# ---------------------------------------------------#

SummaryTable1 = StateHS_Data %>%
  summarise( 
    "Public Schools" = sum(StateHS_Data$CHARTER == "No" & StateHS_Data$MAGNET == "No", na.rm = T),
    "Charter Schools" = sum(StateHS_Data$CHARTER == "Yes", na.rm = T),
    "Magnet Schools" = sum(StateHS_Data$MAGNET == "Yes", na.rm = T),
    "Title 1 Schools" = sum(StateHS_Data$TITLE_1_WIDE == "Yes", na.rm = T),
    " " = " ",
    "  " = "  ",
    "Students" = round(mean(StateHS_Data$STUDENTS, na.rm = T), 0),
    "Teachers" = round(mean(StateHS_Data$TEACHERS, na.rm = T), 0),
    "Student-Teacher Ratio" = round(mean(StateHS_Data$RATIO, na.rm = T), 0)
  )
# ---------------------------------------------------#
# Designing and organizing table
# ---------------------------------------------------#


Summary1 <- kbl(SummaryTable1, caption = "Table 1. State Education Summary Statistics", align = "c") %>%
  add_header_above(c("School Types (Counts)" = 4, 
                     " " = 2,
                     "School Demographics (Means)" = 3)) %>%
  row_spec(0, bold = TRUE) %>% 
  kable_paper("hover", font_size = 16, full_width = TRUE) %>%
  kable_styling(html_font = "Cambria", row_label_position = "c") %>%
  row_spec(0, bold = T, color = "white", background = "#acacac")

# ---------------------------------------------------#
# Printing the summary tables
# ---------------------------------------------------#

Summary1
```

---

## State ACT Descriptive Plots

```{r, echo = F, fig.align='center'}
# ---------------------------------------------------#
# Formatting and designing each bar chart
# ---------------------------------------------------#

# Composite Score - 2019 
a = barch_data %>%
  arrange(CompScore_2019) %>%
  mutate(State = factor(State, levels = State)) %>%   
  ggplot(aes(x = State, y = CompScore_2019)) +
  geom_segment(aes(xend = State , yend = 0), lwd = 1.5, color = "gray") +
  scale_y_continuous(limits = c(0, 36), breaks = c(0, 12, 24, 36)) +
  geom_text(aes(label = CompScore_2019), vjust = 3) +
  geom_point(size = 6, color = "orange") +
  labs(x = "State", y = "Average ACT Composite Score", 
       title = "Figure 1. Composite Score Comparison Chart") +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(size = 16, face = "bold"), panel.background = element_blank(),
        axis.title.x = element_text(size=14),    
        axis.title.y = element_text(size=14),
        axis.text = element_text(face="bold", size = 12))
  
# English Score - 2019
b = barch_data %>%
  arrange(EngScore_2019) %>%    
  mutate(State = factor(State, levels = State)) %>% 
  ggplot(aes(x = State, y = EngScore_2019)) +
  geom_segment(aes(xend = State , yend = 0), lwd = 1.5, color = "gray") +
  scale_y_continuous(limits = c(0, 36), breaks = c(0, 12, 24, 36)) +
  geom_text(aes(label = EngScore_2019), vjust = 3) +
  geom_point(size = 6, color = "red") +
  labs(x = "State", y = "Average English Score", 
       title = "Figure 2. English Score") +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(size = 14, face = "bold"), panel.background = element_blank(),
        axis.title.x = element_text(size=12),    
        axis.title.y = element_text(size=12),
        axis.text = element_text(face="bold", size = 10))

# Math Score - 2019
c = barch_data %>%
  arrange(MathScore_2019) %>% 
  mutate(State = factor(State, levels = State)) %>% 
  ggplot(aes(x = State, y = MathScore_2019)) +
  geom_segment(aes(xend = State , yend = 0), lwd = 1.5, color = "gray") +
  scale_y_continuous(limits = c(0, 36), breaks = c(0, 12, 24, 36)) +
  geom_text(aes(label = MathScore_2019), vjust = 3) +
  geom_point(size = 6, color = "blue") +
  labs(x = "State", y = "Average Math Score", 
       title = "Figure 3. Math Score") +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(size = 14, face = "bold"), panel.background = element_blank(),
        axis.title.x = element_text(size=12),    
        axis.title.y = element_text(size=12),
        axis.text = element_text(face="bold", size = 10))

# Science Score - 2019
d = barch_data %>%
  arrange(ScienceScore_2019) %>% 
  mutate(State = factor(State, levels = State)) %>% 
  ggplot(aes(x = State, y = ScienceScore_2019)) +
  geom_segment(aes(xend = State , yend = 0), lwd = 1.5, color = "gray") +
  scale_y_continuous(limits = c(0, 36), breaks = c(0, 12, 24, 36)) +
  geom_text(aes(label = ScienceScore_2019), vjust = 3) +
  geom_point(size = 6, color = "darkgreen") +
  labs(x = "State", y = "Average Science Score", 
       title = "Figure 4. Science Score") +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(size = 14, face = "bold"), panel.background = element_blank(),
        axis.title.x = element_text(size=12),    
        axis.title.y = element_text(size=12),
        axis.text = element_text(face="bold", size = 10))

# Reading Score - 2019
e = barch_data %>%
  arrange(ReadScore_2019) %>% 
  mutate(State = factor(State, levels = State)) %>% 
  ggplot(aes(x = State, y = ReadScore_2019)) +
  geom_segment(aes(xend = State , yend = 0), lwd = 1.5, color = "gray") +
  scale_y_continuous(limits = c(0, 36), breaks = c(0, 12, 24, 36)) +
  geom_text(aes(label = ReadScore_2019), vjust = 3) +
  geom_point(size = 6, color = "yellow") +
  labs(x = "State", y = "Average Reading Score", 
       title = "Figure 5. Reading Score",
       caption = "Data derives from the 2019 ACT cohort.") +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(size = 14, face = "bold"), panel.background = element_blank(),
        axis.title.x = element_text(size=12),    
        axis.title.y = element_text(size=12),
        axis.text = element_text(face="bold", size = 10))

# ---------------------------------------------------#
# Printing the summary tables and organizing across page
# ---------------------------------------------------#

a
(b | c) / (d | e)
```
